---
title: "White Wine Quality Analysis"
author: "Arvind Raj"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
setwd("D:/Studies/Git/White-wine-Quality")

library(ggplot2)
library(knitr)
library(gridExtra)
library(GGally)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
wwine <- read.csv('wineQualityWhites.csv')
```

This report explores the quality of 4898 different white wines. This particular dataset consists of 4898 observations with 13 different variables.

#Summary of Dataset

```{r echo=FALSE, message=FALSE, warning=FALSE, summary_1}
dim(wwine)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, summary_2}
str(wwine)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, summary_3}
summary(wwine)
```

# Univariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots}
p1 = ggplot(aes(x = fixed.acidity), data = wwine) +
  geom_histogram()
p2 = ggplot(aes(x = volatile.acidity), data = wwine) +
  geom_histogram()
p3 = ggplot(aes(x = citric.acid), data = wwine) +
  geom_histogram()
p4 = ggplot(aes(x = residual.sugar), data = wwine) +
  geom_histogram()
p5 = ggplot(aes(x = chlorides), data = wwine) +
  geom_histogram()
p6 = ggplot(aes(x = free.sulfur.dioxide), data = wwine) +
  geom_histogram()
p7 = ggplot(aes(x = total.sulfur.dioxide), data = wwine) +
  geom_histogram()
p8 = ggplot(aes(x = density ), data = wwine) +
  geom_histogram()
p12 = ggplot(aes(x = pH), data = wwine) +
  geom_histogram()
p9 = ggplot(aes(x = sulphates), data = wwine) +
  geom_histogram()
p10 = ggplot(aes(x = alcohol), data = wwine) +
  geom_histogram()
p11 = ggplot(aes(x = factor(quality)), data = wwine) +
  geom_bar()

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p12, p9, p10, p11, ncol = 3)
```

The one thing we observed in almost all the above plots are the obscene outliers. For further exploration we would have to remove these outliers. We have to cut off the top 1% of data to remove such outliers. The outliers must be cut off from the following variables (fixed acidity, volatile acidity, citric acid, residual sugar, chlorides, free sulfur dioxide, total sulphur dioxide and sulphates.)

```{r echo=FALSE, message=FALSE, warning=FALSE, Remove_outliers}
wwine <- wwine[wwine$fixed.acidity < quantile(wwine$fixed.acidity, 0.99),]
wwine <- wwine[wwine$volatile.acidity < quantile(wwine$volatile.acidity, 0.99),]
wwine <- wwine[wwine$citric.acid < quantile(wwine$citric.acid, 0.99),]
wwine <- wwine[wwine$residual.sugar < quantile(wwine$residual.sugar, 0.99),]
wwine <- wwine[wwine$chlorides < quantile(wwine$chlorides, 0.99),]
wwine <- wwine[wwine$free.sulfur.dioxide < quantile(wwine$free.sulfur.dioxide, 0.99),]
wwine <- wwine[wwine$total.sulfur.dioxide < quantile(wwine$total.sulfur.dioxide, 0.99),]
wwine <- wwine[wwine$sulphates < quantile(wwine$sulphates, 0.99),]
```

# Univariate Analysis



# Bivariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, summary_1}
tmpdata <- wwine[ , !names(wwine) %in% c("X")]
ggcorr(tmpdata, label = TRUE)
```

As we can see from the above plot, it is evident that the quality of the wine corralates with the variables alcohol, density and chloride.

Other than that we can see a strong correlation between 
* Residual sugar and Density 
* total sulfur dioxide and free sulphur dioxide
* total sulfur dioxide and density

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_1}
ggplot(aes(x = density, y = residual.sugar), data = wwine) +
  geom_point(alpha = 0.3, color = 'red', size = 1) +
  geom_smooth(method = 'lm', color = 'green', se = FALSE, size=1)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_2}
ggplot(aes(x = factor(quality), y = alcohol), data = wwine) +
  geom_boxplot(alpha = 0.5, color = 'blue') +
  geom_jitter(alpha = 0.2, color = 'yellow') +
  stat_summary(fun.y = median, geom = 'point', size = 4, shape = 8)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_3}
ggplot(aes(x = factor(quality), y = density), data = wwine) +
  geom_boxplot(alpha = 0.5, color = 'blue') +
  geom_jitter(alpha = 0.2, color = 'yellow') +
  stat_summary(fun.y = median, geom = 'point', size = 4, shape = 8)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_4}
ggplot(aes(x = factor(quality), y = chlorides), data = wwine) +
  geom_boxplot(alpha = 0.5, color = 'blue') +
  geom_jitter(alpha = 0.2, color = 'yellow') +
  stat_summary(fun.y = median, geom = 'point', size = 4, shape = 8)
```


# Bivariate Analysis



# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis



------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Summary

