---
title: "White Wine Quality Analysis"
author: "Arvind Raj"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
setwd("D:/Studies/Git/White-wine-Quality")

library(ggplot2)
library(knitr)
library(gridExtra)
library(GGally)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
wwine <- read.csv('wineQualityWhites.csv')
```

This report explores the quality of 4898 different red wwines. This particular dataset consists of 4898 observations with 13 different variables.

#Summary of Dataset

```{r echo=FALSE, message=FALSE, warning=FALSE, summary_1}
dim(wwine)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, summary_2}
str(wwine)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, summary_3}
summary(wwine)
```

# Univariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots}
p1 = ggplot(aes(x = fixed.acidity), data = wwine) +
  geom_histogram()
p2 = ggplot(aes(x = volatile.acidity), data = wwine) +
  geom_histogram()
p3 = ggplot(aes(x = citric.acid), data = wwine) +
  geom_histogram()
p4 = ggplot(aes(x = residual.sugar), data = wwine) +
  geom_histogram()
p5 = ggplot(aes(x = chlorides), data = wwine) +
  geom_histogram()
p6 = ggplot(aes(x = free.sulfur.dioxide), data = wwine) +
  geom_histogram()
p7 = ggplot(aes(x = total.sulfur.dioxide), data = wwine) +
  geom_histogram()
p8 = ggplot(aes(x = density ), data = wwine) +
  geom_histogram()
p12 = ggplot(aes(x = pH), data = wwine) +
  geom_histogram()
p9 = ggplot(aes(x = sulphates), data = wwine) +
  geom_histogram()
p10 = ggplot(aes(x = alcohol), data = wwine) +
  geom_histogram()
p11 = ggplot(aes(x = quality), data = wwine) +
  geom_bar()

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p12, p9, p10, p11, ncol = 3)
```

The one thing we observed in almost all the above plots are the obscene outliers. For further exploration we would have to remove these outliers. We have cut off the top 1% of data to remove such outliers. The outliers must be cut off from the following variables (fixed acidity, volatile acidity, citric acid, residual sugar, chlorides, free sulfur dioxide, total sulphur dioxide and sulphates.)

```{r echo=FALSE, message=FALSE, warning=FALSE, Remove_outliers}
wwine <- wwine[wwine$fixed.acidity < quantile(wwine$fixed.acidity, 0.99),]
wwine <- wwine[wwine$volatile.acidity < quantile(wwine$volatile.acidity, 0.99),]
wwine <- wwine[wwine$citric.acid < quantile(wwine$citric.acid, 0.99),]
wwine <- wwine[wwine$residual.sugar < quantile(wwine$residual.sugar, 0.99),]
wwine <- wwine[wwine$chlorides < quantile(wwine$chlorides, 0.99),]
wwine <- wwine[wwine$free.sulfur.dioxide < quantile(wwine$free.sulfur.dioxide, 0.99),]
wwine <- wwine[wwine$total.sulfur.dioxide < quantile(wwine$total.sulfur.dioxide, 0.99),]
wwine <- wwine[wwine$sulphates < quantile(wwine$sulphates, 0.99),]
```

# Univariate Analysis

### What is the structure of your dataset?

### What is/are the main feature(s) of interest in your dataset?

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

### Did you create any new variables from existing variables in the dataset?

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?


# Bivariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, summary_1}
tmpdata <- wwine[ , !names(wwine) %in% c("X")]
ggcorr(tmpdata, label = TRUE)
```

```{r echo=FALSE, Bivariate_Plots}

```

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

